\documentclass[11pt]{article}
\usepackage{mathtools}
\usepackage{mdframed}
\usepackage{fullpage}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage{fancyhdr}
\usepackage{lastpage}


%edit this for each class
\newcommand\name{John Collin Vincent}
\newcommand\classname{Com S 352}
\newcommand\assignment{Homework 1}


\newcounter{excounter}
\setcounter{excounter}{1}
\newcommand\ques[2]{\vskip 1em  \noindent\textbf{\arabic{excounter}\addtocounter{excounter}{1}.} \emph{#1} \noindent#2}
\newenvironment{question}{\ques{}\begin{quote}}{\end{quote}}
\newenvironment{subquestion}[1]{#1) \begin{quote}}{\end{quote}}

\pagestyle{fancy}
\rfoot{\name, page \thepage/\pageref{LastPage}}
\cfoot{}
\rhead{}
\lhead{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}


\begin{document}


  {\bf \classname \hspace{1cm} \assignment\hfill \name}
  \vskip 2em


  \begin{question}
    \begin{subquestion}{a}
      \begin{subquestion}{1}
        users may be able to view and take other users files and information.
      \end{subquestion}
      \begin{subquestion}{2}
        if permissions for users/groups are not configured properly users may be able to edit system configuration files and compramise the whole environment
      \end{subquestion}
    \end{subquestion}
    \begin{subquestion}{b}
      you can have a high level of security in a time shared environment with proper permission settings, but the fact that you are regularly letting third parties preform operations on
      the time shared machine creates a inherintly more vulnerable environment than a dedicated machine for each user.
    \end{subquestion}
  \end{question}

  \begin{question}
    users who are collaberating on a project, or have a need for a uniform environment that can be changed by another team to consistently mirror the production envirnment will find a 
    time shared machine more efficient than multiple dedicated machines. 
  \end{question}

  \begin{question}
    symmetric multiprocessing is where there are multiple cpu's that all have the same architecture and are managed by a single OS with some shared memory. asymmetric multiprocessing is where there are multiple cpu's that 
    may or may not have the same architecture and may or may not be running the same OS, they all have a method of communication between them but do not have a shared memory pool.
    \begin{subquestion}{advantages}
      1) users can run multiple process's at a time
      2) users can run different architectures together like a cpu and gpu
      3) speed of execution
    \end{subquestion}
    \begin{subquestion}{disadvantages}
      its hard to sychronize the processors and make them work together in a consistant and stable way.
    \end{subquestion}
  \end{question}

  \begin{question}
    an interrupt is used to signal to the cpu that a hardware process has finished and is ready to be handled. An interrupt is different from a trap in that a trap is thrown by a user
    program and is often the result of a division by 0 or an invalid memory access. yes traps can be thrown intentionally and are often used to switch context mode.
  \end{question}

  \begin{question}
    The cpu sends a request to the DMA controlled to initiate the transfer. An interrupt is triggered to alert the cpu when the memory process is complete.
  \end{question}

\end{document}
